InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex

>>>>

The first image generative model we use is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

As a second image generative model we use OpenDalle from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.

This is done in two steps: 
\begin{enumerate}
	\item The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer.
	\item BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
\end{enumerate}

The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}

We choose the GPT2 model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}

The \textbf{Falcon-RW-1B} model built by TII (\url{https://www.tii.ae/}) is the second text generative model we use to test our augmentation models. It is a decoder-only model trained on 350 billion tokens of the RefinedWeb data set. This data set leverages strict filtering and stringent deduplication to uplift the quality of web data. \cite{penedo2023refinedweb}
